Simulating High-Dimensional Multivariate Data

### 2021-02-26 040-monte-carlo-evaluation.Rmd

```{r ch040-LoadLib040, include=FALSE}
devtools::load_all()
library(tidyverse)
## library(bigsimr)
## Sys.setenv(JULIA_NUM_THREADS = parallel::detectCores())
## bs <- bigsimr_setup()
## dist <- distributions_setup()
```

>>>>

```{r ch040-LoadLib040, include=FALSE}
box::use(
    dplyr[...],
    ggplot2[...],
    patchwork[...],
    tidyr[pivot_longer],
    bigsimr[bigsimr_setup, distributions_setup],
    knitr[include_graphics]
)
load("data/bivariate_normal_sims.rda")
load("data/bivariate_gamma_sims.rda")
load("data/bivariate_nbinom_sims.rda")

load("data/benchmark_dependences.rda")

Sys.setenv(JULIA_NUM_THREADS = parallel::detectCores())
bs <- bigsimr_setup(pkg_check = FALSE)
dist <- distributions_setup()
set.seed(10162020)
prob <- 3e-04
```

### 2021-02-26 050-examples.Rmd

```{r ch050-LoadLib, include=FALSE, cache=FALSE}
devtools::load_all()
library(tidyverse)
library(patchwork)
library(bigsimr)

@@

cores <- as.integer(parallel::detectCores() - 1)
set.seed(10142020)
```

@@

```{r ch050-figBRCA, out.width='80%', fig.cap="Simulated random vectors from a multivariate negative binomial replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters from simulated data (vertical axes) and the specified target parameters (horizontal axes)."}
knitr::include_graphics('fig/ch050-figBRCA.png')
```

>>>>

```{r ch050-LoadLib, include=FALSE, cache=FALSE}
box::use(
  dplyr[...],
  ggplot2[...],
  patchwork[...],
  bigsimr[...],
  knitr[include_graphics]
)
load("data/example_brca.rda")
load("data/example_genes.rda")

@@

set.seed(10142020)
```

@@

```{r ch050-figBRCA, out.width='80%', fig.cap="Simulated random vectors from a multivariate negative binomial replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters from simulated data (vertical axes) and the specified target parameters (horizontal axes)."}
include_graphics('fig/ch050-figBRCA.png')
```
